Case-based Arabic Morphological Analyzer for Arabic Text Mining

### 2010-12-20 tex/rp.tex
novelty, fine editing, new bibs

\lfoot{QNRF Form}
\cfoot{}
\rfoot{Page \thepage~of~\pageref{LastPage} }
\renewcommand{\footrulewidth}{0.2pt}
\renewcommand{\headrulewidth}{0.2pt}

@@

The almost comprehensive book 
``Arabic Computational Morphology''~\cite{Sou07}
covers most academic research work on Arabic text mining.
It summarizes recent work, and presents strong evidence of 
shortage of historic research. It also highlights  an emerging 
interest with a specific application to machine 
translation from Arabic to English after 2001.
The research community showed little interest in 
automating Arabic text analysis that may serve
the Arabic user.
While machine translation is of general interest, 
an Arabic user is more interested in 
information hard to discover manually.
Examples are the relation between clinical records, pharmaceutical 
prescriptions and sales, and a specific sickness,
the relation
between stock prices and political news, or the 
relation between interrogation reports with suspects
and investigative reports from the crime scenes.

We propose to build a framework for
%{\em relational text mining 
%of Arabic using morphological and case-based analysis}. 
{\em case-based Arabic text analysis using relations and morphology} (CATARM). 
CATARM will apply novel algorithms and tools
to answer queries seeking relations amongst
Arabic text documents.
CATARM takes as input several sets of documents, each of a specific
type, and a user query. % expressed in a visual language.
The query, expressed in a visual language, allows the user 
to build a flow of Arabic text mining
components and discover desired relations between documents. 
CATARM compiles the query into a netlist of computational 
components. It also uses features extracted from the query and 
the document sets to simplify the computational 
components. 
%The main CATRAM computational components will be finite 
%state machines (FSM) that express a linguistic model of the Arabic 
%language and that can be parametrized and relaxed to fit a case 
%study.

@@

ElixirFM~\cite{Otakar:07} uses an {\em inferential-realizational}
approach for morphological analysis
and considers the form of the word 
\noTrRL{.sarf}  instead of its segments. 
Formal rules express the relations between 
the root of the lexeme and the fully inflected word. 
While the rules capture features unique to the 
the Arabic language and its linguistic description~\cite{Badawi:04},
the approach is computationally expensive and enumerates 
all the possible solutions.

@@

We describe CATARM using four case studies and then move
to describe the different tools needed to build
CATARM.

@@

The biography books are fed to another MA unit controlled by 
a name and qualification pair controller that generates a 
map consisting of pairs of narrator names associated with 
qualifications. 
Then the graph of narrators and the narrator qualification map
are both processed through a locator component that computes
a graph coloring routine to color the graph of narrators. 
The color changes when two consecutive narrators are far away
from each other in the text. 
The locator then looks at connected subgraphs of the same color,
and finds a median node in each of them to be the narrator 
associated with the qualifiers of the color. 
Then the locator also annotates the narrator with the 
corresponding qualifications. 
The result is an annotated partial order graph of narrators
with authentication qualification annotations.

@@

As such reports contain sensitive information and our contacts
in the Lebanese security declined direct access, 
we will start the security case study by studying dummy documents that 
represent both interrogative and investigative types of documents. 
We collected a small amount (in the order of tens)
of similar documents published in the news in the last two years
from cases that were brought to public court or from high profile
cases that leaked to the media.
We will work on augmenting this collection further to have a large
enough set of reports (in the order of hundreds). 
We will mutate the entities in these documents and seed the mutated
set with relations we wish to discover and that are hard to discover
manually. 
Later on, we will use our contacts with the Lebanese and Qatari 
security authorities
to validate our system on their real data.

@@

Parental controls help parents allow their kids to benefit from the internet 
without fearing the danger of violent and obscene material. 
These controls partially rely on processing the content to detect and rate 
the target material. 
Control mechanisms for Arabic traffic as currently mostly manual. 
In this case study we will detect the bad content. 
Given a set of undesired internet content 
and a set of requests by internet users, 
CATARM can discover whether there is a relation between 
the requested documents and the undesired content and flag the 
requested document with strong enough relation.

@@

We will work with our contacts at the American University
Hospital (AUH) at Beirut to analyze this data and relate it
to nearby pharmaceutical records.

@@

Toutanova in~\cite{Tou09} suggested that using 
a joint model to do lemmatization and POS tagging performs better
than the direct and the pipelined approach. 
We take the first argument further to suggest a full joint NLP task 
model via using the NLP query to simplify and render the analysis
more accurate at the low level morphological analysis.

@@

Our LCM will differ from ElixirFM~\cite{Otakar:07}
in that it will follow a relational approach rather 
than a functional morphological approach. 
That is the solutions will be expressed in a directed acyclic graph 
(DAG)
representing a hierarchy of relations between the morphemes 
rather than moprhological trees mapping the morphemes to the 
solutions.
We think this is better since it provides a more succint
representation for the solutions and because interesting relations 
between morphemes can be computed statically before
the input is presented to the analyzer.
Morphological trees are traversals of these DAGs, are expensive 
to exhaustively compute and store statically, 
and are expensive to compute dynamically. 
Our intuition is that Arabic allows relational strcutures
such as noun sentences and complex hierarchical entities.

@@

In ~\cite{Dao09}, Daoud observes that the pipeline model,
where morphology is performed first and syntactic and other
processes follow, is not adequate for Arabic. 
He suggests a synchronized syntactic and morphological
approach.  
We take the argument further to 
allow a tighter integration between the several pipeline
levels up to the NLP query in question by providing a 
case-based morphological analyzer, a linguistic computational
model of Arabic, and a query language that can all be expressed
as FSMs. 
The work~\cite{AlSham08} reports a similar result where
the automated addition of syntax knowledge improved steeming
in terms of accuracy and efficiency.

Here we point to a subtletie that shows how complex 
low level Arabic morphology is. 
The work in~\cite{Dao09} assumes that a noun
cannot be followed by a preposition in Arabic and uses that 
to resolve an ambiguity in the 
example~\noTrNoVocRL{.s-a.hb-aa s-amy _dhb-aa il_A alswq} 
(Sami's two companions went to the market) 
    and decides that \noTrNoVocRL{_dhb-aa} 
is a verb (they went)
and not a noun since it is followed by \noTrNoVocRL{il_A}.
One can 
say~\noTrNoVocRL{a_h_d  .s-a.hb-aa s-amy _dhb-aa il_A alswq} 
(Sami's two companions took gold to the market) and 
now \noTrNoVocRL{_dhb-aa} is a noun (gold stressed with double 
diactric).
This shows that even complex and advanced techniques such as
~\cite{Dao09} can be misled by ambiguous compatibility
rules.

@@

This task is not trivial though, since $\rho_q$ may contain
states and transitions that are not always morphemes and 
transitions between morphemes. 
We will consider a hierarchical methodology that follows 
the hierarchical structure of the Arabic language expressed
in $L_A$. 
Consider $\Phi$ the state machine representing the grammar 
rules for $L_A$ and consider $\phi$ the parse graph 
representing $\rho_q$, in particular consider the atomic nodes 
representing lexical entries in $\phi$. 
Consider $S$ to be the set of states in $\Phi$ that 
correspond to these nodes. 
Consider simplifying $\Phi$ using techniques that remove 
states and transitions that do not lead to $S$. 
An optimal reduction requires expensive reachability 
analysis, however, we can apply simpler reductions such 
as structural cone of influence reduction,
constant propagation reduction that overapproximate
reachability analysis. 
%For example, we may consider sets of connected states in $\rho_q$ 
%containing a single morpheme as a state in one hierarchy level 
%in $L_A$.
We will perform this simplification before starting the 
morphological analysis since we already have to analyze
the query $q$ and compute $\rho_q$ before we start
the analysis.

@@

We will follow an eXtreme Programming 
methodology in the process of building CATARM.
This means that we will define refined incremental items of 
work that allows for more frequent deliverables. 
This also means that the code base will always be subject
to maintenance and refactoring to enhance reuse and 
increase productivity. 
While a item is delivered, it will still be subject to work,
enhancements, and maintenance.

@@

That said, we describe the dependency of the items on 
each other as follows. 
The work on language optimizations and data optimizations 
depend on the Arabic LCM item. 
The work on language optimizations depends on the design
of the query language as well. 
The work on the query solver depends on the design of the 
query language. 
The entity and relation extractors depend on the morphological 
analyzer. 
However, they can start since we have already
developed an working analyzer as a preliminary step. 
The rest of the items can all work in parallel.

We will use open source tools, libraries, and frameworks to 
build our componenets.
We will build on existing open source programming and text 
mining tools as well as open source Arabic text analysis tools 
based on NLP such as MADA+TOKAN~\cite{Rot08}, 
NEMLAR~\cite{RAl09}, and IJAES~\cite{Int09}.

@@

@@

The team will seek the assistance and help of an independent 
consultant in the middle of the second and third years of 
the duration of the project to evaluate and validate the results.

@@

If granted, this project will initiate a long term
research relationship between Qatar University
and the American University of Beirut. 
Once completed, the Arabic text analysis framework will be 
an open source contribution and developers from the Arabic 
world in the open source community are expected to join 
efforts to keep it going.
Furthermore, the Arabic text analysis framework 
can sustain itself by charging on support or expert use.

The framework or service on the framework can easily be 
commercialized to tend to the security, health, insurance, market,
news, media, or literature business sectors.

@@

The completion of the CATARM framework will result in a 
significant contribution to the research community of 
NLP in general and Arabic Analysis in particular. 
The CATARM framework will act as vehicle to enhance and advance 
research in the area. 
We look forward for additional contributions to the field 
such as the following.
\begin{itemize}
\item We will explore developing and integrating vocalization
techniques. 
Vocalization techniques assign diacritics to unvocalized text. 
The prerequisites of a successful vocalizer are the accuracy of 
the morphological analyzer in addition to grammatical analyzers. 
\item We will explore the use of CATARM with more case studies
such as market analysis and opinion mining.
\item We will explore augmenting the lexicon of the
morphological analyzer with useful categorization and entity 
tags that reflect semantical meanings. 
These modifications would give CATARM additional capabilities in 
terms of allowing users to extract and use a greater variety of 
entities when building queries. 
The feedback of experts in the field of Arabic linguistics can 
continually add accuracy to the morphological solutions.  
\item We will explore further optimization techniques
that can help simplify and the analysis. 
\item We will explore generalizing our results to languages 
that resemble the Arabic language. 
Some Semitic languages, such as the Amharic, Cyrillic, and Hebrew,
share common features with the Arabic 
language. Some other languages are written using the 
Arabic script like Persian, Kurdish, Urdu, and Pashto. 
\item We will also investigate the case-based approach with
Latin languages and check how that compares with current techniques
in terms of accuracy and efficiency.
\item We will maintain CATARM and provide support to users and 
researchers of CATARM.
\end{itemize}

@@

The team will publish the results of the research in the form 
of refereed conference and journal papers as well as tool papers 
addressing each of the tools. 
The team will also hold workshops to educate possible users on the 
tools once the tools are available.
Graduate students such as Masters and PhD students are examplary t
target audience for such workshops.
The Arabic text analysis framework will be partially based on 
existing work in the open source domain and will thus be available 
as an open source tool. 
Interested researchers and users will be able to download the 
tools for free and use them for non-profit non-commercial 
purposes.

\pagebreak
%\bibliography{adnan_refs}
%\bibliographystyle{ieeetr}
\bibliographystyle{abbrvnat}
%\bibliographystyle{ieeetr}
{\small
\bibliography{fzAr}  
}

>>>>

\lfoot{QNRF Form}
\cfoot{}
%\rfoot{Page \thepage~of~\pageref{LastPage} }
\rfoot{Page \thepage~of~23}
\renewcommand{\footrulewidth}{0.2pt}
\renewcommand{\headrulewidth}{0.2pt}

@@

The almost comprehensive book 
``Arabic Computational Morphology''~\cite{Sou07}
covers substantial academic research work on Arabic text mining.
It summarizes recent work, and presents strong evidence of 
shortage of historic research. It also highlights  an emerging 
interest with a specific application to machine 
translation from Arabic to English after 2001.
The research community showed little interest in 
automating Arabic text analysis that may serve
the Arabic user.
While machine translation is of general interest, 
an Arabic user is more interested in 
information hard to discover manually.
Examples are the relation between clinical records, pharmaceutical 
prescriptions and sales, and a specific sickness,
the relation
between stock prices and political news, or the 
relation between interrogation reports with suspects
and investigative reports from the crime scenes.

We propose to build a framework for
%{\em relational text mining 
%of Arabic using morphological and case-based analysis}. 
{\em case-based Arabic text analysis using relations and morphology} (CATARM). 
CATARM will apply novel algorithms and tools
to answer queries seeking relations amongst
Arabic text documents.
CATARM takes as input several sets of comparable documents, 
each of a specific
type, and a user query. % expressed in a visual language.
The query, expressed in a visual language, allows the user 
to build a flow of Arabic text mining
components and discover desired relations between documents. 
CATARM compiles the query into a netlist of computational 
components. It also uses features extracted from the query and 
the document sets to simplify the %computational 
components. 
%The main CATRAM computational components will be finite 
%state machines (FSM) that express a linguistic model of the Arabic 
%language and that can be parametrized and relaxed to fit a case 
%study.

@@

ElixirFM~\cite{Otakar:07} uses an {\em inferential-realizational}
approach for morphological analysis
and considers the form of the word 
\noTrRL{.sarf}  instead of its segments. 
Formal rules express the relations between 
the root of the lexeme and the fully inflected word. 
While the rules capture features unique to 
the linguistic description of Arabic~\cite{Badawi:04},
the approach is computationally expensive and enumerates 
all the possible solutions.

@@

We describe CATARM using four case studies and then move
to describe the different tools needed to build
CATARM.
We chose our case studies to be documents of comparable
content. 
Our intuition is that this is more 
adequate to a relational text mining approach.

@@

The biography books are fed to another MA unit controlled by 
a name and qualification pair controller that generates a 
map consisting of pairs of narrator names associated with 
qualifications. 
Then the graph of narrators and the narrator qualification map
are both processed through a locator component that computes
a graph coloring routine to color the graph of narrators. 
The color changes when two consecutive narrators are far away
from each other in the text. 
The locator then looks at connected subgraphs of the same color,
and finds a median node in each of them to be the narrator 
associated with the qualifiers of the color. 
Then the locator also annotates the narrator with the 
corresponding qualifications. 
The result is an annotated partial order graph of narrators
with authentication qualification annotations. 
The digitized hadith and biography books are available 
online~ \footnote{We obtained
  the digitized books from online sources such as 
  \href{http://www.yasoob.com/}{http://www.yasoob.com/} and 
  \href{http://www.al-eman.com/}{http://www.al-eman.com/}. }.
The books are considered open Islamic heritage and access to
them is granted without considerable IP constraints. 
We are looking at processing around 60 books of hadith and
biographies each in several volumes. 
The total data size is in the order of 30MB worth of digital 
data.

@@

As such reports contain sensitive information and our contacts
in the Lebanese security declined direct access, 
we will start the security case study by studying dummy documents that 
represent both interrogative and investigative types of documents. 
We collected a small amount (in the order of tens)
of similar documents published in the news in the last two years
from cases that were brought to public court or from high profile
cases that leaked to the media.
We will work on augmenting this collection further to have a large
enough set of reports (in the order of hundreds). 
We will mutate the entities in these documents and seed the mutated
set with relations we wish to discover and that are hard to discover
manually. 
We are looking at processing original documents in the order
of hundreds, and at generating few tens of thousands of dummy 
documents.
Later on, we will use our contacts with the Lebanese and Qatari 
security authorities
to validate our system on their real data.

@@

Parental controls help parents allow their kids to benefit 
from the Internet 
without fearing the danger of violent and obscene material. 
These controls partially rely on processing the content to detect 
and rate the target material. 
Control mechanisms for Arabic traffic as currently mostly manual. 
In this case study we will detect the bad content. 
Given a set of undesired Internet content 
and a set of requests by Internet users, 
CATARM can discover whether there is a relation between 
the requested documents and the undesired content and flag the 
requested document with strong enough relation. 
The undesired content is available online and is in the 
order of thousands of documents. 
We will look at Arabic Internet traffic five times larger to
validate our case study.

@@

We will work with our contacts at the American University
Hospital (AUH) at Beirut to analyze this data and relate it
to nearby pharmaceutical records. 
The data available is in the order of few thousand clinical reports
and comparable pharmaceutical records.

@@

Toutanova in~\cite{Tou09} suggested that using 
a joint model to do lemmatization and part of speech (POS
tagging performs better
than the direct and the pipelined approach. 
We take the first argument further to suggest a full joint NLP task 
model via using the NLP query to simplify and render the analysis
more accurate at the low level morphological analysis.

@@

Our LCM will differ from ElixirFM~\cite{Otakar:07}
in that it will follow a relational approach rather 
than a functional morphological approach. 
That is the solutions will be expressed in a directed acyclic graph 
(DAG)
representing a hierarchy of relations between the morphemes 
rather than morphological trees mapping the morphemes to the 
solutions.
We think this provides a more succinct
representation for the solutions.
Also interesting relations 
between morphemes can be computed statically before
the input is presented to the analyzer.
Morphological trees are traversals of these DAGs, are expensive 
to exhaustively compute and store statically, 
and are expensive to compute dynamically. 
Our intuition is that Arabic allows relational structures
such as noun sentences and complex hierarchical entities.

@@

In ~\cite{Dao09}, Daoud observes that the pipeline model,
where morphology is performed first and syntactic and other
processes follow, is not adequate for Arabic. 
He suggests a synchronized syntactic and morphological
approach.  
We take the argument further to 
allow a tighter integration between the several pipeline
levels up to the NLP query in question by providing a 
case-based morphological analyzer, a linguistic computational
model of Arabic, and a query language that can all be expressed
as FSMs. 
The work~\cite{AlSham08} reports a similar result where
the automated addition of syntax knowledge improved stemming
in terms of accuracy and efficiency.

Here we point to a subtlety that shows how complex 
low level Arabic morphology is. 
The work in~\cite{Dao09} assumes that a noun
cannot be followed by a preposition in Arabic and uses that 
to resolve an ambiguity in the 
example~\noTrNoVocRL{.s-a.hb-aa s-amy _dhb-aa il_A alswq} 
(Sami's two companions went to the market) 
    and decides that \noTrNoVocRL{_dhb-aa} 
is a verb (they went)
and not a noun since it is followed by \noTrNoVocRL{il_A}.
One can 
say~\noTrNoVocRL{a_h_d  .s-a.hb-aa s-amy _dhb-aa il_A alswq} 
(Sami's two companions took gold to the market) and 
now \noTrNoVocRL{_dhb-aa} is a noun (gold stressed with double 
diactric).
This shows that even complex and advanced techniques such as
~\cite{Dao09} can be misled by ambiguous compatibility
rules.

@@

This task is not trivial though, since $\rho_q$ may contain
states and transitions that are not always morphemes and 
transitions between morphemes. 
We will consider a hierarchical methodology that follows 
the hierarchical structure of the Arabic language expressed
in $L_A$. 
Consider $\Phi$ the state machine representing the grammar 
rules for $L_A$ and consider $\phi$ the parse graph 
representing $\rho_q$, in particular consider the atomic nodes 
representing lexical entries in $\phi$. 
Consider $S$ to be the set of states in $\Phi$ that 
correspond to these nodes. 
Consider simplifying $\Phi$ using techniques that remove 
states and transitions that do not lead to $S$. 
An optimal reduction requires expensive reachability 
analysis, however, we can apply simpler reductions such 
as structural cone of influence and
constant propagation reductions that overapproximate
reachability analysis. 
This simplification is Arabic specific since
the query language matches the structure of question sentences 
in common standard Arabic.
In addition, the query itself reflects the way an Arabic user
himself thinks and searches. 
%For example, we may consider sets of connected states in $\rho_q$ 
%containing a single morpheme as a state in one hierarchy level 
%in $L_A$.
We will perform this simplification before starting the 
morphological analysis since we already have to analyze
the query $q$ and compute $\rho_q$ before we start
the analysis.

@@

We will follow a relaxed  eXtreme Programming 
methodology in the process of building CATARM.
This means that we will define refined incremental items of 
work that allows for more frequent deliverables. 
This also means that the code base will always be subject
to maintenance and refactoring to enhance reuse and 
increase productivity. 
While an item is delivered, it will still be subject to work,
enhancements, and maintenance. 
We selected eXtreme Programming as this fits well in the 
context of research where the clients are at close 
contact with the developers.
It accomodates the high dependency amongst the 
modules of CATARM. 
The pair programming practice in eXtreme Programming 
works well in the context of academy and research to keep
expertise in the team. 
As senior students graduate, their junior partners in the pair
will keep the knowledge in.

@@

That said, we describe the dependency of the items on 
each other as follows. 
The work on language optimizations and data optimizations 
depend on the Arabic LCM item. 
The work on language optimizations depends on the design
of the query language as well. 
The work on the query solver depends on the design of the 
query language and on the availability of the entity and relation
extractors. 
The entity and relation extractors depend on the morphological 
analyzer. 
However, they can start since we have already
developed an working analyzer as a preliminary step. 
The rest of the items can all work in parallel.

We will use open source tools, libraries, and frameworks to 
build our components.
We will build on existing open source programming and text 
mining tools as well as open source Arabic text analysis tools 
based on NLP such as MADA+TOKAN~\cite{Rot08}, 
NEMLAR~\cite{RAl09}, and IJAES~\cite{Int09}.

@@

\subsection{Novelty}

We claim the novelty of the following items
\begin{itemize}
\item the case-based morphological analyzer,
\item the flexible and partial linguistic computational model,
\item the language specific LCM simplification techniques,
\item the application of language independent statistical techniques
to simplify the LCM,
\item the solutions of the four proposed case studies,
\item and the CATRAM framework as an integration of all the above techniques.
\end{itemize}

@@

The team will seek the assistance and help of independent 
consultants  in the middle of the second and third years of 
the duration of the project to evaluate and validate the results.

@@

If granted, this project will initiate a long term
research relationship between Qatar University
and the American University of Beirut. 
Once completed, the Arabic text analysis framework will be 
an open source contribution and developers from the Arabic 
world in the open source community are expected to join 
efforts to keep it going.

The PIs will continue soliciting funds for the development
of extensions and enhancements of this work as well.

Furthermore, the Arabic text analysis framework 
can partially sustain itself by charging on support or expert use
similar to other similar projects such as the ATB.
The framework or service of the framework can be 
commercialized to tend to commercial usage from 
the security, health, insurance, market,
news, media, or literature business sectors.

@@

The completion of the CATARM framework will result in a 
significant contribution to the research community of 
NLP in general and Arabic Analysis in particular. 
The CATARM framework will act as vehicle to enhance and advance 
research in the area. 
We look forward for additional contributions to the field 
such as the following.
\begin{itemize}
\item We will explore developing and integrating vocalization
techniques. 
Vocalization techniques assign diacritics to unvocalized text. 
The prerequisites of a successful vocalizer are the accuracy of 
the morphological analyzer in addition to grammatical analyzers. 
\item We will explore the use of CATARM with more case studies
such as market analysis and opinion mining.
\item We will explore augmenting the lexicon of the
morphological analyzer with useful categorization and entity 
tags that reflect semantic meanings. 
These modifications would give CATARM additional capabilities in 
terms of allowing users to extract and use a greater variety of 
entities when building queries. 
The feedback of experts in the field of Arabic linguistics can 
continually add accuracy to the morphological solutions.  
\item We will explore further optimization techniques
that can help simplify and the analysis. 
\item We will explore generalizing our results to languages 
that resemble the Arabic language. 
Some Semitic languages, such as the Amharic, Cyrillic, and Hebrew,
share common features with the Arabic 
language. Some other languages are written using the 
Arabic script like Persian, Kurdish, Urdu, and Pashto. 
\item We will also investigate the case-based approach with
Latin languages and check how that compares with current techniques
in terms of accuracy and efficiency.
\item We will maintain CATARM and provide support to users and 
researchers of CATARM.
\end{itemize}

@@

The Arabic text analysis framework will be partially based on 
existing work in the open source domain and will thus be available 
as an open source tool. 
Interested researchers and users will be able to download the 
tools for free and use them for non-profit non-commercial 
purposes.  
The tools we have developed so far are readily available 
online under the {\em atmine} project~\cite{ATMine09}.

The team will publish the results of the research in the form 
of refereed conference and journal papers as well as tool papers 
addressing each of the tools. 
We already submitted one manuscript describing the case-based
morphological analyzer. 
We have a ready to publish manuscript on the hadith authentication
case study. 
We plan to have publications on each of the 
linguistic computational model, the language specific techniques
to simplify it, and the language independent techniques to simplify
it. 
We also plan to have a publication on each of the separate case 
studies. 
We plan to have technical reports, tool papers, and user
guides describing
the whole CATARM framework and its use.

The team will also hold workshops to educate possible users of the
tools at AUB, QU, and in other places of interest. 
Masters,  PhD, and senior undergraduate students are 
exemplary target audience for such workshops.

\pagebreak
\rfoot{Page \thepage~of~\pageref{LastPage} }
%\bibliography{adnan_refs}
%\bibliographystyle{ieeetr}
\bibliographystyle{abbrvnat}
%\bibliographystyle{ieeetr}
{\small
\bibliography{fzAr}  
}
